%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Solution Architect \& Analytics Developer} % Job title
{Telia Company} % Organization
{Stockholm, Sweden} % Location
{Mar. 2016 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item Working with \textbf{Data Pipelines} for \textbf{Crowd Analytics}, Network Data (probes, CDRs), \textbf{IPTV} 
\item Architecting and implementing \textbf{data ingestion}, storage, compression and archival strategies in a multi-tenant kerberized Data Lake
\item Leading the move from \textbf{Map-Reduce, Hive jobs to Spark}
\item Optimized Spark code for data anonymization for Crowd Analytics \textbf{(10x Speedup)}
\item Optimization of Cloudera Hadoop Cluster \textbf{(small files issues, block size issues, slow Hive queries, slow MR jobs)}
\item Spark application development
\item Data discovery using Jupyter/Zeppelin notebooks
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Systems Engineer} % Job title
{Tradedoubler AB} % Organization
{Stockholm, Sweden} % Location
{Sep. 2015 - Feb. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item Setup/administration of \textbf{Hortonworks cluster} in \textbf{Google Compute Cloud}
\item Design and architecture of data pipelines (DropWizard, Kafka, Storm, HDFS, Parquet, Spark)
\item Spark application development
\item Data discovery using ipython/zeppelin notebooks
\end{cvitems}
}

%------------------------------------------------

\cventry
{Systems Engineer} % Job title
{PDC Center for HPC, KTH} % Organization
{Stockholm, Sweden} % Location
{Jan. 2013 - Aug. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item Design and deploy highly scalable cloud-based SaaS infrastructure (OpenStack).
\item Administration of Ceph Cluster and integration with Openstack cloud
\item Writing \href{https://github.com/ezhaar/spark-openstack}{software} and \href{https://github.com/ezhaar/spark-installer}{scripts} to support creation of \textbf{virtual clusters} for data intensive computing on our private cloud. 
\item Virtualization (IAAS, PAAS) on \textbf{OpenStack, AWS}
\item \textbf{Docker} for \textbf{Hadoop} and \textbf{Spark} dev environments
\item Advance \textbf{OpenVPN} deployment
\end{cvitems}
}

%------------------------------------------------

\cventry
{Systems Engineer, Freelance Consultant (side project)} % Job title
{Nosiva AB} % Organization
{Stockholm, Sweden} % Location
{Feb. 2015 - Jul. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item Setup \textbf{BigData infrastructure} in \textbf{AWS}
\item Administration of \textbf{Hadoop and Spark} Clusters in AWS 
\item Setup development environment (data exploration) for data scientists \textbf{jupyter notebooks, spark, cassandra}
\item Spark application development (python)
\item Development of Services to handle \textbf{streaming data} from \textbf{Amazon Kinesis}
\item Service deployment using \textbf{docker} 
\end{cvitems}
}

%------------------------------------------------

\cventry
{Research Engineer} % Job title
{PDC Center for HPC, KTH} % Organization
{Stockholm, Sweden} % Location
{Jun. 2009 - Dec. 2012} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item Provide support for \textbf {MPI, OpenMP} and \textbf{CUDA} Programming applications on PDC clusters.
\item Worked with \textbf{Cray XE6} system (35000+ cores)
\item Management and installation of software on HPC Clusters.
\item Developed dashboard for monitoring, accounting of jobs on PDC clusters (\textbf{Django, MySQL, JQuery, HighCharts}).
\item Collaboration with researchers to develop and \textbf{optimize parallel applications}.
\item Developed and updated documentation for end users on how to use HPC resources.
\item Provided technical support and training to new users and employees.
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
